\begin{thebibliography}{99}

% BOOK
\bibitem{feedback_system} Karl Johan Astrom, Richard M. Murray, \emph{Feedback Systems: An Introduction for Scientists and Engineers}, Princeton University Press, 2012.

\bibitem{intergral_lqr} A Joukhadar, I Hasan, A Alsabbagh, M Alkouzbary, \emph{Integral Lqr-Based 6dof Autonomous Quadrocopter Balancing System Control}, International Journal of Advanced Research in Artificial Intelligence, Vol. 4, No.5, 2015.

\bibitem{manual_tunning} Nur Hayati Sahrir, Mohd Ariffanan Mohd Basri, \emph{Modelling and Manual Tuning PID Controlof Quadcopter}, Control, Instrumentation and Mechatronics: Theory and Practice (pp.346-357).

\bibitem{calculus} Nguyễn Đình Huy, \emph{Giáo trình giải tích 1}, Đại học Quốc gia TP. Hồ Chí Minh, 2020.

\bibitem{MultiGyro} Faisal Iqbal, Hussamud Din, Byeungleul Lee, \emph{Single Drive Multi-Axis Gyroscope with High Dynamic Range, High Linearity and Wide Bandwidth}, Micromachines 2019, 10(6), 410.

\bibitem{LQR} Heja Cengiz, \emph{Quadcopter Modeling and Linear Quadratic Regulator Design Using Simulink}, Uppsala Universitet, 2024.

% ARTICLE
\bibitem{IAEME} Ha Quang Thinh Ngo, Thanh Phuong Nguyen, Hung Nguyen, "A COMPLETE COMPARISON TO DESIGN COMPLEMENTARY FILTER AND KALMAN FILTER FOR AERIAL VEHICLE", \emph{International Journal of Mechanical Engineering and Technology}, 2018.

\bibitem{robotics_contrl} Rio Ikhsan Alfian, Alfian Ma'arif, Sunardi Sunardi, "Noise Reduction in the Accelerometer and Gyroscope Sensor with the Kalman Filter Algorithm", \emph{Journal of Robotics and Control (JRC)}, 2021.

\bibitem{discretePID} Luis E. Romero, David F. Pozo, Jorge A. Rosales, "Quadcopter Stabilization by Using PID Controllers", \emph{ACADEMIA}, 2014.

\bibitem{gyrophone} Yan Michalevsky, Dan Boneh, "Gyrophone: Recognizing Speech from Gyroscope Signals", \emph{Proceedings of the 23rd USENIX Security Symposium}, 2014.
\bibitem{lqr_handout} Dennis Freeman, Kevin Chen "Linear quadratic regulator (LQR) control" Source: https://introcontrol.mit.edu/\_static/spring23/lectures/lec08a-handout.pdf.
% MISC
\bibitem{mpudatasheet} "MPU-6000 and MPU-6050 Product Specification Revision 3.4", 2013. Source: www.invensense.com.

\bibitem{Mpu_guide_code} "Hướng dẫn sử dụng cảm biến gia tốc MPU6050 với Arduino", 2023. Source: https://arduinokit.vn/huong-dan-su-dung-cam-bien-gia-toc-mpu6050-voi-arduino/.

\bibitem{tkinter} "tkinter — Python interface to Tcl/Tk". Source: https://docs.python.org /3/library/tkinter.html.

\bibitem{socket} "socket — Low-level networking interface". Source: https://docs.python.org /3/library/socket.html.

\bibitem{arduino} "Arduino Documentation". Source: https://docs.arduino.cc/.

\bibitem{ultraSonic} "Distance Measurement with an Ultrasonic Sensor HY-SRF05", 2017. Source: https://projecthub.arduino.cc/Nicholas\_N/distance-measurement-with-an-ultrasonic-sensor-hy-srf05-bf2923.

\bibitem{escCalibrate} "ESC Calibration". Source: https://ardupilot.org/plane/docs/common-esc -calibration.html.

\bibitem{quadcop} Wikipedia, "Quadcopter". Source: https://en.wikipedia.org/wiki/Quadcopter.

\bibitem{gyro} STMicroelectronics, "Everything about STMicroelectronics’ 3-axis digital MEMS gyroscopes". Source: https://www.elecrow.com/download/TA0343.pdf.

\bibitem{Modellingandcontrol} Teppo Luukkonen, "Modelling and control of quadcopter". Source: https://sal.aalto.fi/publications/pdf-files/eluu11\_public.pdf.

\bibitem{acc} "Accelerometer and Gyroscopes Sensors: Operation, Sensing, and Applications". Source: https://www.analog.com/en/resources/technical-articles/accelerometer-and-gyroscopes-sensors-operation-sensing-and-applications.html.

\bibitem{MultiGyro2} "Single Drive Multi-Axis Gyroscope with High Dynamic Range, High Linearity and Wide Bandwidth". Source: https://www.mdpi.com/2072-666X/10/6/410.

\bibitem{kalmantutor} Michel van Biezen, "SPECIAL TOPICS 1 - THE KALMAN FILTER". Source: https://www.youtube.com/watch?v=CaCcOwJPytQ\&list=PLX2gX-ftPVXU3oUFNATxGXY90AULiqnWT\&index=1.

\bibitem{Self-Stabilizing} Kevin Jordan, "Self-Stabilizing Quadcopter UAV Using PID Control: Full Control Systems Project Presentation". Source: https://www.youtube.com/watch?v=clyusOrMqbU.

\bibitem{GyroWork2} Curio Res, "How Gyroscope Sensor Works? | 3D Animated". Source: https://www.youtube.com/watch?v=HJ-C4Incgpw.

\bibitem{DesignImplement} Blue Butterfly, "How to design and implement a digital low-pass filter on an Arduino". Source: https://www.youtube.com/watch?v=REVp33SwwHE.

\bibitem{quadEquationYoutube} Dr. KC Craig, "Quadrotor Equations of Motion and Control KCC Final 4 2023 Video". Source: https://www.youtube.com/watch?v=REVp33SwwHE.

\bibitem{I2C} thegioiic, "Tìm hiểu về chuẩn giao tiếp I2C". Source: https://www.thegio iic.com/tin-tuc/tim-hieu-ve-chuan-giao-tiep-i2c.

\bibitem{PWM} Timothy Hirzel, "Basics of PWM (Pulse Width Modulation)". Source: https://do cs.arduino.cc/learn/microcontrollers/analog-output/.

\bibitem{CarbonAeronautics} Carbon Aeronautics, "Carbon Aeronautics Quadcopter Manual". Source: https://github .com/CarbonAeronautics/Manual-Quadcopter-Drone/blob /main/Carbon\_Aeronautics\_Quadcopter\_Manual.pdf.

\bibitem{FlySky} LinhKienRC, "Combo điều khiển TX – RX Flysky FS i6". Source: https://bando choi.net/combo-dieu-khien-tx-rx-flysky-fs-i6.html.

\bibitem{ESP8266} nshopvn, "Module thu phát Wifi ESP8266 NodeMCU Lua CP2102". Source: https://nshopvn.com/product/module-thu-phat-wifi-esp8266-nodemcu-lua-cp2102/.

\bibitem{Teensy} Sam Market, "Teensy 4.0 (Headers)". Source: https://market.samm.com/teensy-4-0 -headers-en.

\bibitem{MPU6050} hshop, "Cảm biến GY-521 6DOF IMU MPU6050". Source: https://hshop.vn /cam-bien-6-dof-bac-tu-do-gy-521-mpu6050.

\bibitem{BMP280} nshopvn, "Cảm biến áp suất IIC I2C và nhiệt độ của BMP280 3.3 V". Source: https://nshopvn.com/product/cam-bien-ap-suat-iic-i2c-va-nhiet-do-cua-bmp280-3-3-v/.

\bibitem{ESC30A} Nguyễn Hiền, "Mạch điều khiển tốc độ động cơ không chổi than ESC 30A 4V-16V (Pin 2S-4S) BEC 5V". Source: https://dientunguyenhien.vn/show/3252.

\bibitem{A2212} nshopvn, "Động cơ không chổi than A2212". Source: https://nshopvn.com /product/dong-co-khong-choi-than-a2212/.

\bibitem{ESP8266FPT} FPT Jetking, "ESP8266 là gì? Tìm hiểu về module Wi-Fi phổ biến cho IoT". Source: https://jetking.fpt.edu.vn/esp8266/.

\bibitem{TeensyUARTPort} pjrc, "Using the Hardware Serial Ports". Source: https://www.pjrc.com/teensy/td \_uart.html

\bibitem{OnOff} x-engineer, "On-off control system". Source: https://x-engineer.org/on-off-control- system

\bibitem{Accel} webOS TV Developer, "Sensor Data for Motion Sensor". Source: https:// webostv.developer.lge.com/develop/guides/motion-sensor-sensor-data.

\bibitem{Atadiat} Yahya Tawil, "Towards understanding IMU: Basics of Accelerometer and Gyroscope Sensors and How to Compute Pitch, Roll and Yaw Angles". Source: https://atadiat.com/en/e-towards-understanding-imu-basics-of-accelerometer-and-gyroscope-sensors/.

\bibitem{Dynamic} Nasser M. Abbasi, "Dynamics equations, kinematics, velocity and acceleration diagrams". Source: https://www.12000.org/my\_notes/dynamics\_cheat\_sheet/ reportchapter2.htm.

\end{thebibliography}